\section{Pilot Test}
The pilot test was conducted on a single participant which served the purpose of giving us some feedback on how we can improve the test setup.
One of the bigger things was that the coding part of the test took two hours rather than the one hour we had intended despite skipping one of the tasks.
Following the pilot test we made several changes to our setup:
\begin{itemize}
\item Task 1 in the task sheet was largely rewritten to have more concrete examples and to try and focus on the simpler calculations.
This was due to our participant starting to spend a lot of time working on constructs for a larger shopping system instead of focusing on the arithmetic core of the task we had intended.
\item Task 2 was shortened from 5 subtasks to three subtasks due to the repetitive nature of the subtasks and to cut down on time spent.
\item The participant skipped task 3(now task 4) due to its similarity with task 2 which caused us to swap its position with task 4(now task 3).
This was also helped by the observation that getting data about classes in Quorum was deemed more important than operations on strings.
\item In the discussion the access modifiers for methods and properties in classes was brought up which caused us to realise this was not discussed in the sample sheet.
Some description and examples of access modifiers for classes was then added to the end of the sample sheet.
\item When conducting the interview we realised that we were unprepared as we did not know what we wanted to discuss.
This caused us to create the interview questions to provide a guideline for things to discuss.
\end{itemize}