\input{./text/method/Introduction}
\chapter{Design considerations}
The concept of programming is essentially devising a mental plan for solving a particular problem and transforming that into a workable solution by making use of some programming language. The solution to a problem might vary for different implementations since different paradigms have different approaches, but usually the essence of said solution does not change. Devising a set of programming tasks which are not targeted at a specific language implementation is a daunting task since many paradigms have to be taken into account at the same time. Additionally, the tasks have to be interesting and engaging enough so that the participants can focus on the solution. As described previously in section \todo{previous section with the RPG task goes here}, for our usability experiment we devised one big task with several subtasks for the C\# part, each as a prerequisite for the next one. It followed the theme of a role playing game and it mainly revolved around the use of inheritance. The second task, addressing F\#, was still modelled as a game and it revolved around a robot finding a goal in a world of tiles, essentially relying on the use of recursion as a concept. Although we did not count time as an important factor in our experiment, we still had to put a specific time constraints on how long a participant can work on the tasks. The main reason for that is our aim is process-oriented rather than result-oriented, which make it easier for programming language designers in the future to replicate our experiment. Based on the feedback from the participants, we got a better estimate of how much time each task takes for its completion and how relevant it is in the given context. Furthermore, this served as a stepping stone towards gaining a better understanding of how to design tasks with more general context i.e. being solvable in more than one programming paradigm. 
\\\\For our evaluation method, we devised several smaller tasks, each addressing different features and constructs of the selected language - in this case Quorum. We drew heavy inspiration for some of the tasks from Codekata \cite{Codekata} since some of the katas were simple to understand yet conveyed the essence of a particular feature. 
\input{./text/method/setup/ConductingTheEval}
\input{./text/method/results/ResultsDiscussion}